---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# macrobonder

The goal of macrobonder is to provide simple funtions to read data from
the Macrobond.

The macrobonder depends on the MacrobondAPI. 

## Installation

To install the MacrobondAPI see: https://help.macrobond.com/technical-information/the-macrobond-api-for-r/.

To install the macrobonder:

```{r install, eval=FALSE}

# install.packages("devtools")
devtools::install_github("pttry/macrobonder")

```



## Get data from macrobond

There are two functions to get data from the Macrobond:

* `get_md()`, simpler and faster method to get whole series with same frequency.
* `get_convert_mb()`, a method with more options to get also series with
   different frequency. Series are converted to same frequancy.
   
Series are returned as a data.frame.

### get_md()

```{r example_get}
suppressPackageStartupMessages(library(macrobonder))

x <- get_mb(series = c("usgdp", "figdp"))

str(x)

```

Series can be also named:

```{r named_example}

x <- get_mb(series = c(usa = "usgdp", finland = "figdp"))

str(x)


```


### get_convert_md()

```{r example_get_convert}

y <- get_convert_mb(series = c("usgdp", "uscpi"), frequency = "Annual")

str(y)

```
